\section{Limitations and Future Work}\label{sec:limitationsandfuturework}

One major issue is that this project is depending strongly on the quality of the data available at \url{Meetup.com}. We have to rely on the users of \url{Meetup.com} so this issue can hardly be improved. One idea would be to integrate other social services like \url{Facebook.com} to extrend our data source and to get more independent. In this way one could also fix the problem that \url{Meetup.com} might be less known in non-English speaking countries. Having a wide base as data source one gets more independent of local and regional preferences regarding the social networks.

We should also keep in mind that we only retrieved data for \emph{open} events. So far it is not possible to access all events in a city because for most of them you have to be a member of specific groups. 

Another problem is that this project has the potential to be extended in the following way: So far our program is restricted to predefined cities. It is not possible to select new cities or regions. This is due to the fact that we work with GeoJSON-files which are saved locally on the hard drive. One improvement could be to create a user interface and the possibility to select new cities and regions. By selecting single categories of events one could get special information, e.g. where to go running. Additional, in an application, one could automatically create suitable graphics, charts and tables.\\Another limitation is as well related to \url{Meetup.com}. Since we only have one data source for events, we only can give sufficient criterions for districts. A district having lots of events seems to be trending. However, a district having less events is not automatically less interesting and popular. It just means that its inhabitants are not using \url{Meetup.com}. Again, one should take more data sources into account.\\One further aspect could be to look for interest of twitter users to make recommendations to activities nearby. The geotag of the tweets provides the central information for the search.

Our tool could help social scientists to prove their hypothesis with the provided data. Beside literature, studies and surveys our tool seems to be a good method for analyzing the behaviour and preferences of populations.